When you are submitting your code be sure to include all your files. \textbf{This includes copies of the files which were initially provided to you}. Include alongside your code files, a short video of you explaining the code and the associated test bench results. All new files or substantially modified files must have an associated test bench. Please ensure that the code you provide demonstrates each of the functionalities required of the design. Include copies of the block diagrams created in order to plan the design. 

\begin{itemize}
    \item The video needs to walk through all the functions required of the design. Showing the simulation results for each test bench. The audio is clearly understandable, and the language is concise yet descriptive. The video cannot exceed 5 minutes. \begin{flushright}
        \framebox[1.1\width]{\underline{\hspace{1cm}}\textbackslash2\%}
    \end{flushright}
    
    \item The submitted code is complete and synthesizes to a bitstream file. All the test benches can be run and have built in checks for functionality. The constraints file maps correctly to the Basys 3 board. When the bitstream is generated it creates a playable game, include any instructions for additional required hardware or configuration in your submission. \begin{flushright}
    
        \framebox[1.1\width]{\underline{\hspace{1cm}}\textbackslash1\%}
    \end{flushright}
    \item The design is well commented. Explanations of the elements are included in each file. The code is written in a way that suggests that the design has been planned out from the beginning. \begin{flushright}
    
        \framebox[1.1\width]{\underline{\hspace{1cm}}\textbackslash1\%}
    \end{flushright}
    \item There is a completed design record showing that the design meets the 100MHz clock alongside block diagrams of each major element of the design, as well a top level block diagram. State the maximum clock frequency for your design and show the calculations (using the WNS) \begin{flushright}
        \framebox[1.1\width]{\underline{\hspace{1cm}}\textbackslash1\%}
    \end{flushright}
    
\end{itemize}