Your marks are split evenly between your code and the explainer video.\\
\begin{itemize}
    \item Include all the required files for your design and test benches. This means that all the System Verilog Files are present even if they are unmodified. Also be sure to include the associated constraints file.
    \item Ensure the provided code produces an led pattern at a speed which is clear at human time-scales. 
    \item Include a design report file. This should include your timing constraints and a calculation of the maximum operating frequency for your design. It also needs to include a screenshot of your RTL view after making the modifications. Your report should have a cover page containing your Name, Student ID, Lab Section, and Lab Title. 
    \item \textbf{Create a timing diagram showing pulse width modulation and explaining why it can be used to produce a dimming effect with LEDs. Include this in your design report alongside the other material}. Feel free to use tools like  \url{https://wavedrom.com/} to produce your timing diagrams. If using one of these tools make sure to include the text used to generate the waveform diagram. 
    \item Record a short 1-3 minute video explaining what you have done. Look at each segment of your code and explain approximately how it is working. 
\end{itemize}

\vspace{0.5cm}
Provide a video of you walking through each section of your code and explaining your reasoning. Your video should be no more than 4 minutes long. Ensure that you are clearly audible through the video. 