When you are submitting your code be sure to include all your files. \textbf{This includes copies of the files which were initially provided to you}. Include alongside your code files, a short video of you explaining the code and the associated test bench results. Please ensure that the code you provide demonstrates each of the functionalities required of the design. Include copies of the block diagrams created in order to plan the design. 

\begin{itemize}
    \item The video walks through all the functions required of the design. Showing the simulation results for each test bench.
    \item The submitted code is complete and synthesizes to a bit stream file. All the test benches can be run and have built in checks for functionality. 
    \item There is a complete design record showing that the design meets the timing requirements. 
    \item A block diagram has been provided for each major section. The block diagram may be drawn either by hand or using a diagramming language or an open source mark down language such as mermaid \url{https://github.com/mermaid-js/mermaid}. % \textbf{Students are welcome to use ChatGPT to assist with creating their block diagrams }
\end{itemize}

\subsection*{Code Quality and Functionality (5 Points)}

\begin{enumerate}
    \item \textbf{Clarity and Organization}: Code is well-organized, making it easy to follow. (1 point)
    \item \textbf{Commenting}: Code is sufficiently commented to explain complex or non-intuitive portions. (1 point)
    \item \textbf{Functionality}: All required functionalities are implemented in the code. (1 point)
    \item \textbf{Test Benches}: Test benches are comprehensive and cover all aspects of the design. Built-in checks for functionality are present. (1 point)
    \item \textbf{Synthesizability}: The code synthesizes to a bit-stream file without errors. (1 point)
\end{enumerate}

\subsection*{Documentation (2 Points)}

\begin{enumerate}
    \item \textbf{Design Record}: Complete record showing that the design meets the timing requirements. (1 point)
    \item \textbf{Block Diagrams}: A block diagram is included for each major section of the design. Diagrams can be hand-drawn or generated through a diagramming language like Mermaid. (1 point)
\end{enumerate}

\subsection*{Video Walkthrough (3 Points)}

\begin{enumerate}
    \item \textbf{Clarity}: The video is clear and easy to follow. (1 point)
    \item \textbf{Coverage of Functionalities}: The video walks through all required functionalities. (1 point)
    \item \textbf{Simulation Results}: The video shows simulation results for each test bench. (1 point)
\end{enumerate}
