This is an examination TAs are not allowed to help you, you are guiding them through the project, explaining the reasoning behind your design. 

\begin{itemize}
    \item The Design is presented clearly and cleanly with a logical process being followed. \hspace{1cm} \_\_:1\%
    \item The Design is fully functional with no apparent glitches in the design behavior. \hspace{1cm} \_\_:1\%
    \item The student can show a clear understanding of functionality of various block components in thier design. \hspace{1cm} \_\_:1\%
    \item The student can explain the functionality of a piece of code in their design when asked, explaining how it fits into the larger context of the design. \hspace{1cm} \_\_:2\%
\end{itemize}

\vspace{1cm}

\begin{itemize}
    \item The TA will come to your table and ask you to explain the design to them. You will have 5 minutes to walk the TA through your design. This can be done on a white board, through a presentation, or through walking them through the Vivado project. This presentation should take no more than 5 minutes.\\
    \item The TA will then ask the student to close Vivado entirely on their system and then load their design onto the Basys 3 board.
    \item The TA will spend 1-2 minutes going through the design functionality on the board. The student can explain their button and switch assignments.
    \item The TA will then ask the student to explain a component, chosen by the TA on the block diagram. The student will need to explain the functionality of the sub-component and how it works in the broader context of the design.
    \item The TA will then go to a random section of the students code and ask them to explain how it functions. If the code is extensively documented it is valid for the student to read the comments written in the code to explain the functionality. 
    
\end{itemize}

